---
title: 'Fuzzy Operations'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Triangular Norms (T-norms)

### Four t-norms functions are implemented in the **t-norms.R** script: 

- Minimum
- Product
- Lukasiewicz
- Drastic Product

```{r}
source("t-norms.R")
```

### A = ($min_A, mean_A, max_A$) and B = ($min_B, mean_B, max_B$) are triangular fuzzy numbers represented by three points: minimum, mean and maximum values

```{r}
fuzzy.number.a = c(min.value = 1, mean.value = 4, max.value = 6)
fuzzy.number.b = c(min.value = 3, mean.value = 5, max.value = 7)
```

### The **plot.tnorms** function gives the plot of all T-norms 

```{r}
plot.tnorms(fuzzy.number.a, fuzzy.number.b)
```

### Minimum T-norm

```{r}
plot.tnorms(fuzzy.number.a, fuzzy.number.b, "min")
```

### Product T-norm

```{r}
plot.tnorms(fuzzy.number.a, fuzzy.number.b, "pro")
```

### Lukasiewicz T-norm

```{r}
plot.tnorms(fuzzy.number.a, fuzzy.number.b, "luka")
```

### Drastic Product T-norm

```{r}
plot.tnorms(fuzzy.number.a, fuzzy.number.b, "dra")
```

## Triangular Conorms (S-norms)

### Four t-norms functions are implemented in the **s-norms.R** script: 

- Maximum
- Probabilistic sum
- Bounded sum (Lukasiewicz)
- Drastic sum

```{r}
source("s-norms.R")
```

### The **plot.snorms** function gives the plot of all S-norms

```{r}
plot.snorms(fuzzy.number.a, fuzzy.number.b)
```

### Maximum S-norm

```{r}
plot.snorms(fuzzy.number.a, fuzzy.number.b, "max")
```

### Probabilistic sum S-norm

```{r}
plot.snorms(fuzzy.number.a, fuzzy.number.b, "pro")
```

### Bounded sum (Lukasiewicz) S-norm

```{r}
plot.snorms(fuzzy.number.a, fuzzy.number.b, "bound")
```

### Drastic sum S-norm

```{r}
plot.snorms(fuzzy.number.a, fuzzy.number.b, "dra")
```
